How South Koreans View Democracy?

### 2024-04-18 paper/paper.qmd
update

---
title: "Exploring Democratic Perceptions in South Korea"
subtitle: "An Analysis of Survey Data in 2016"
author: 
  - Hailey Jang 
thanks: "Code and data are available at: https://github.com/Hailey-Jang/How_South_Koreans_View_Democracy.git."
date: today
date-format: long
abstract: "This study explores the impact of globalization on democratic values and participation in South Korea by employing a linear regression model to analyze responses from a nationwide questionnaire on citizens' perceptions and engagement. It found that economic disparities and transformative political changes significantly influence citizens’ views on democracy and their participation levels. Through this quantitative analysis, the research uncovers a complex relationship between socio-economic factors and democratic perception, demonstrating how economic inequalities can diminish feelings of representation and reduce democratic participation. These findings underscore the importance of addressing economic and social inequalities to foster a more inclusive and participative democratic environment in South Korea, contributing to our broader understanding of how globalization shapes political systems worldwide."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "How South Koreans View Democracy?"
subtitle: "An Analysis of Survey Data in 2016"
author: 
  - Hailey Jang 
thanks: "Code and data are available at: https://github.com/Hailey-Jang/How_South_Koreans_View_Democracy.git."
date: today
date-format: long
abstract: "This study explores the impact of globalization on democratic values and participation in South Korea by employing a linear regression model to analyze responses from a nationwide questionnaire on citizens' perceptions and engagement. It found that economic disparities and transformative political changes significantly influence citizens’ views on democracy and their participation levels. Through this quantitative analysis, the research uncovers a complex relationship between socio-economic factors and democratic perception, demonstrating how economic inequalities can diminish feelings of representation and reduce democratic participation. These findings underscore the importance of addressing economic and social inequalities to foster a more inclusive and participative democratic environment in South Korea, contributing to our broader understanding of how globalization shapes political systems worldwide."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
